Verifying Demonstrations

### 2019-02-28 paper/distance-bounding.tex
Minor clarification on TF-resistance in distance-bounding

There are four adversaries for \ac{DB} protocols established in the literature, 
each of which tries to commit a type of fraud.
These can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
    possibly honest, prover who is far away from the verifier.
    (Also known as relaying attack or man-in-the-middle attack.)
  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
    who is close to the verifier, to authenticate.
    \Ac{DBTF} resistance is a very strong property; it implies that if the 
    accomplice succeeds (with non-negligible probability) he will learn the 
    prover's secret key\footnote{%
      This means that even things like functional encryption will not help.
    }.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
    uses an unsuspecting honest prover close to the verifier to pass as being 
    close.
    (This is different from \ac{DBMF} in that the honest prover actually tries 
    to authenticate to the verifier, but the malicious prover hijacks the 
    channel at some point(s) during the protocol.)
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

>>>>

There are four adversaries for \ac{DB} protocols established in the literature, 
each of which tries to commit a type of fraud.
These can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
    possibly honest, prover who is far away from the verifier.
    (Also known as relaying attack or man-in-the-middle attack.)
  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
    who is close to the verifier, to authenticate.
    \Ac{DBTF} resistance is a very strong property; it implies that if the 
    verifier accepts the accomplice with non-negligible probability the 
    accomplice can compute the prover's secret key\footnote{%
      This means that even things like functional encryption will not help.
    }.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
    uses an unsuspecting honest prover close to the verifier to pass as being 
    close.
    (This is different from \ac{DBMF} in that the honest prover actually tries 
    to authenticate to the verifier, but the malicious prover hijacks the 
    channel at some point(s) during the protocol.)
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
